\documentclass[letterpaper, 10pt]{article}
\usepackage{nopageno}
\usepackage[margin=0.5in]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=0pt, left=0pt}

\begin{document}
\raggedright

\begin{center}
{\LARGE \textbf{Praneeth Rangarajan}}\\
(470) 246-6421 \(\mid\) rangarajanpraneeth@gmail.com \(\mid\) github.com/rangarajanpraneeth \(\mid\) linkedin.com/in/rangarajanpraneeth
\end{center}

\vspace{8pt}
{\large \textbf{EDUCATION}}
\vspace{4pt}
\hrule

\textbf{Georgia State University: College of Arts \& Sciences} \hfill \textit{Class of 2026}\\
Bachelor of Science in Computer Science

\vspace{8pt}
{\large \textbf{PROJECTS}}
\vspace{4pt}
\hrule

\textbf{Co-Evolutionary Financial Market Simulation} \hfill \textit{2025}
\begin{itemize}
    \item Built a multi-agent simulation modeling competitive strategy evolution across 10,000+ market cycles, implementing reinforcement learning algorithms that adapt trading behavior based on profit signals and dynamic feedback.
    \item Created comprehensive visualization and statistical tools to track portfolio performance, measure Sharpe ratios, and observe emergent agent behaviors under 15+ volatility regimes and randomized shock scenarios.
    \item Conducted 50+ controlled experiments varying learning rates, reward structures, and market conditions to study strategy convergence patterns, stability thresholds, and failure modes in adaptive systems.
\end{itemize}

\textbf{Sim Racing Telemetry Dashboard} \hfill \textit{2024 - Present}
\begin{itemize}
    \item Developed a real-time telemetry dashboard that processes 60 Hz vehicle data streams with sub-100 ms latency, displaying precise driver inputs, sector times, tire temperatures, and 20+ dynamic performance metrics.
    \item Implemented lap comparison and consistency analysis tools that identify performance gaps down to 0.01-second precision, pinpointing specific corner entry speeds, braking points, and throttle differences across 100+ laps.
    \item Designed a modular plugin architecture that supports hot-swappable analytics modules and custom visualizations, reducing feature integration time by 60\% without requiring core system modifications.
\end{itemize}

\textbf{Algorithmic Trading Bot} \hfill \textit{2024 - Present}
\begin{itemize}
    \item Built an automated trading system processing real-time market feeds from 5+ exchanges, detecting opportunities through multi-timeframe analysis of price action, order flow dynamics, and volatility patterns.
    \item Implemented a comprehensive backtesting engine that evaluates the performance of the strategy over 3+ years of historical data, measuring win rates, maximum drawdown, risk-adjusted returns, and execution slippage.
    \item Structured the system with an extensive log infrastructure that captures 1000+ daily data points, granular parameter controls, and staged deployment protocols that ensure a safe transition from paper to live trading.
\end{itemize}

\vspace{8pt}
{\large \textbf{EXPERIENCE}}
\vspace{4pt}
\hrule

\textbf{Coding Tutor \(\mid\) Code Hero Academy - Alpharetta, GA} \hfill \textit{Current}
\begin{itemize}
    \item Teach programming fundamentals and problem-solving strategies through structured, hands-on sessions covering core concepts in Python, JavaScript, and algorithm design to students aged 8-16.
    \item Develop interactive coding projects and demonstrations for community events, creating engaging technical showcases that illustrate real-world applications of computer science principles and inspire student interest.
\end{itemize}

\vspace{8pt}
{\large \textbf{SKILLS}}
\vspace{4pt}
\hrule

\textbf{Programming Languages:} JavaScript, Python, C++, SQL, TypeScript\\
\textbf{Tools \& Frameworks:} Node.js, Express.js, Docker, Git, MongoDB, NumPy, Pandas, CCXT

\vspace{8pt}
{\large \textbf{EXTRACURRICULARS}}
\vspace{4pt}
\hrule

\textbf{Fintech Organization at GSU \(\mid\) Georgia State University - Atlanta, GA}
\begin{itemize}
    \item Participate in workshops and technical discussions on financial technology innovations, focusing on digital finance infrastructure, quantitative analytics, and emerging technologies within modern financial systems.
\end{itemize}

\textbf{UGAHacks \(\mid\) University of Georgia - Athens, GA}
\begin{itemize}
    \item Developed functional software prototypes within 24-hour constraints, collaborating with cross-functional teams to design, implement, and iterate practical technical solutions from concept through final demonstration.
\end{itemize}

\textbf{CodeDay \(\mid\) LexisNexis Risk Solutions - Alpharetta, GA}
\begin{itemize}
    \item Built three award-winning prototypes during separate 24-hour CodeDay events, leading end-to-end development from initial concept and architecture through implementation, testing, and final presentation to judges.
\end{itemize}

\end{document}
